---
title: "Writing a great story for data science projects "
subtitle: "This is a Report Template Quarto"
author: "Student Name (Advisor: Dr. Cohen)"
date: '`r Sys.Date()`'
format:
  html:
    code-fold: true
course: Capstone Projects in Data Science
bibliography: references.bib # file contains bibtex for references
#always_allow_html: true # this allows to get PDF with HTML features
self-contained: true
execute: 
  warning: false
  message: false
editor: 
  markdown: 
    wrap: 72
---

Slides: [slides.html](slides.html){target="_blank"} ( Go to `slides.qmd`
to edit)

::: callout-important
**Remember:** Your goal is to make your audience understand and care
about your findings. By crafting a compelling story, you can effectively
communicate the value of your data science project.

Carefully read this template since it has instructions and tips to
writing!

Nice report! I am adding this to show updates from RStudio.
:::

## Introduction

  The military has been using Electronic Warfare (EW) since World War I
[@noauthor_under_nodate]. With recent technological advances, EW will
continue to evolve; most recently, through the military use of drones,
which depend on reliable radio frequency (RF) links and are vulnerable
to jamming and interference [@vgi_admin_drones_2025]. Recently, machine
learning is used to address these threats. For example, Jere et al.
combined supervised learning with Bayesian network inference to detect
and classify jamming in 5G New Radio networks in near real time
[@10352089]. That work shows that Bayesian methods can utilize machine
learning models in wireless security which will be more accurate and
more interpretable [@10352089]. The selection of a signal dataset that
supports both neural network modeling and Bayesian analysis to predict
signal-to-noise ratio (SNR) and examine how signal quality varies across
conditions [@10352089]. 

  Our project uses the DeepSig RadioML 2018.01A
dataset, downloaded from Kaggle, containing simulated RF signals across
different modulation types with varying levels of noise [@OShea2018].
The dataset includes 24 modulation types, 26 SNR levels ranging from −20
dB to +30 dB, and 1,024 in-phase and quadrature (I/Q) samples per
signal, for approximately 2.5 million total observations [@OShea2018].
It therefore provides a useful schema for studying how signal quality
changes under different interference conditions [@OShea2018]. 

  The objective of this project is to model SNR as the response variable using
neural networks and Bayesian analysis. Bayesian methods treat model
parameters as probability distributions rather than fixed values. This
allows prior knowledge to be formally incorporated and results to be
expressed as direct probability statements about quantities of interest
[@Berger01122000]. Applied to neural networks, the Bayesian framework
has a solution to overfitting and ways to quantify uncertainty in
predictions [@Bishop1997]. In addition, Bayesian neural networks are
better than standard networks when data are noisy, because Bayesian
neural networks reports show how confident each prediction is
[@DBLP:journals/corr/abs-1801-07710]. Guidance on using these models
with deep learning tools is explained by Jospin et al. Because the
dataset is large, scalability is an important consideration [@9756596].
Hernández-Lobato et al. studied that "probabilistic backpropagation
allows Bayesian neural networks to be trained efficiently on large
datasets while retaining accurate uncertainty estimates"
[@pmlr-v37-hernandez-lobatoc15]. 

  Because our dataset DeepSig 2018 contains a large number of raw signal 
measurements, feature engineering techniques will be applied to summarize the I/Q components into meaningful predictors. It might be seen that some of the predictors are correlated with one another, so factor sensitivity analysis using
Bayesian neural networks will identify which inputs strongly influence
the predicted SNR [@5376749]. Model performance will be evaluated using
statistics metrics such as mean squared error (MSE). Comparisons will be
made to assess how well regularization methods commonly used in neural
networks handle multicollinearity and improve prediction accuracy. In
the Bayesian setting, prior distributions on network weights act as a
natural form of regularization, comparable to weight decay in
conventional networks [@Bishop1997]. Finally, Bayesian optimization will
be considered for tuning model hyperparameters. Prior work shows that it
can find strong configurations with fewer training runs than grid or
random search [@snoek2015scalable].

## Methods

- Detail the models or algorithms used.

- Justify your choices based on the problem and data.

*The common non-parametric regression model is*
$Y_i = m(X_i) + \varepsilon_i$*, where* $Y_i$ *can be defined as the sum
of the regression function value* $m(x)$ *for* $X_i$*. Here* $m(x)$ *is
unknown and* $\varepsilon_i$ *some errors. With the help of this
definition, we can create the estimation for local averaging i.e.*
$m(x)$ *can be estimated with the product of* $Y_i$ *average and* $X_i$
*is near to* $x$*. In other words, this means that we are discovering
the line through the data points with the help of surrounding data
points. The estimation formula is printed below [@R-base]:*

$$
M_n(x) = \sum_{i=1}^{n} W_n (X_i) Y_i  \tag{1}
$$$W_n(x)$ *is the sum of weights that belongs to all real numbers.
Weights are positive numbers and small if* $X_i$ *is far from* $x$*.*

*Another equation:*

$$
y_i = \beta_0 + \beta_1 X_1 +\varepsilon_i
$$

## Analysis and Results

### Data Exploration and Visualization

- Describe your data sources and collection process.

- Present initial findings and insights through visualizations.

- Highlight unexpected patterns or anomalies.

A study was conducted to determine how...

```{r, warning=FALSE, echo=T, message=FALSE}
reticulate::use_python("/Users/jd/.local/share/virtualenvs/jd-y3HzYupt/bin/python", required = TRUE)
# loading packages 
library(tidyverse)
library(knitr)
library(ggthemes)
library(ggrepel)
library(dslabs)
```

```{python}

import pandas as pd
from data_processing import X_transformed,y
import numpy as np
print(f"Y mean: {y.mean().values[0]}")

```

```{r, warning=FALSE, echo=TRUE}
# Load Data
kable(head(murders))

ggplot1 = murders %>% ggplot(mapping = aes(x=population/10^6, y=total)) 

  ggplot1 + geom_point(aes(col=region), size = 4) +
  geom_text_repel(aes(label=abb)) +
  scale_x_log10() +
  scale_y_log10() +
  geom_smooth(formula = "y~x", method=lm,se = F)+
  xlab("Populations in millions (log10 scale)") + 
  ylab("Total number of murders (log10 scale)") +
  ggtitle("US Gun Murders in 2010") +
  scale_color_discrete(name = "Region")+
      theme_bw()
  

```

### Modeling and Results

- Explain your data preprocessing and cleaning steps.

- Present your key findings in a clear and concise manner.

- Use visuals to support your claims.

- **Tell a story about what the data reveals.**

```{r}

```

### Conclusion

- Summarize your key findings.

- Discuss the implications of your results.

## References